Sell Prevention and Buy Cure: An Exploration of Indirect Conflicts

### 2014-01-13 iced-2013/paper.tex
ICED changed intro for new version.

In order to fully understand the root causes of information overload, false positives, and
scalability issues in regards to indirect conflicts, we conducted an empirical study to determine what events occur to
cause indirect conflicts, when they occur, and if conditions exist to provoke more of these events. 
We then set out to understand what mitigation strategies developers currently use as opposed to those created
by academia. Through this exploration, we look to find what can be accomplished moving forward with indirect conflicts
in both research and industry. To accomplish these goals, we ask the following:

>>>>

In order to investigate the root causes of information overload, false positives, and
scalability issues in regards to indirect conflicts, we conducted an empirical study to determine what events occur to
cause indirect conflicts, when they occur, and if conditions exist to provoke more of these events. 
We then set out to understand what mitigation strategies developers currently use as opposed to those created
by academia. Through this exploration, we look to find what can be accomplished moving forward with indirect conflicts
in both research and industry and how we can get over the road block of these information overload related
issues. To accomplish these goals, we ask the following:
